### 2024-06-04 thesis/appendix.tex
cleaned all problems and warnings

\chapter{Appendix}
\section{Feature map normalisation}\label{appendix:new_feature}

\begin{lemma}
    Associated to any RKHS $\mathcal{H}$, there exists a feature vector $\phi(x)$ such that $\|\phi(x)\|_{\mathcal{H}}=R \quad \forall x \in \mathcal{X}$.
    That is the Hilbert space norm of the feature vector is equal to a constant R for all states in the set $\mathcal{X}$.
\end{lemma}
\begin{proof}
    Taking the new feature vector as $\phi^{new} (x):=\frac{\phi(x)}{\|\phi(x)\|_{\mathcal{H}}}$ we have
\begin{align*}
    \|
    \phi^{new}(x)\|_{\mathcal{H}}^{2} &= \left\|\frac{\phi(x)}{\|\phi(x)\|_{\mathcal{H}}}
    \right\|_{\mathcal{H}}^{2}
    \\
    &=
    \left\|
    \frac{\phi(x)}
    {\sqrt{k(x,x)}}
    \right\|_{\mathcal{H}}^{2}
    \\
    &=
    \left\langle
    \frac{\phi(x)}
    {\sqrt{k(x,x)}}
    ,
    \frac{\phi(x)}
    {\sqrt{k(x,x)}}
    \right\rangle_{\mathcal{H}}
    \\
    &=
    \frac{1}{\sqrt{k(x,x)^{2}}}
    \langle
    \phi(x)
    ,
    \phi(x)
    \rangle_{\mathcal{H}}
    \\
    &=1
\end{align*}
\end{proof}

\section{Quantile regressor extensive comparison}\label{appendix:quantile_regressor_extensive_comparison}
This section contains extensive comparison between our kernel quantile regression and other state of the art quantile regressors. We benchmark it on popular machine learning datasets.
\subsection{Boston housing dataset}
The Boston housing dataset \href{https://www.kaggle.com/datasets/altavish/boston-housing-dataset}{https://www.kaggle.com/datasets/altavish/boston-housing-dataset} contains information about various attributes for suburbs in Boston.
There are 13 indipendent variables
\begin{itemize}
\item CRIM: per capita crime rate by town
\item ZN: proportion of residential land zoned for lots over 25,000 sq.ft.\
\item INDUS: proportion of non-retail business acres per town
\item CHAS: Charles River dummy variable (1 if tract bounds river, 0 otherwise)
\item NOX: nitric oxides concentration (parts per 10 million)
\item RM: average number of rooms per dwelling
\item AGE: proportion of owner-occupied units built prior to 1940
\item DIS: weighted distances to five Boston employment centres
\item RAD: index of accessibility to radial highways
\item TAX: full-value property-tax rate per 10,000
\item PTRATIO: pupil-teacher ratio by town
\item B: $1000(Bk - 0.63)^2$ where Bk is the proportion of afroamericans by town
\item LSTAT: lower status of the population
\end{itemize}
The dependent variable is MEDV, that is the median value of owner occupied homes in \$1000's

@@

\subsection{Vehicle dataset}
This data contains info about used cars \href{https://www.kaggle.com/datasets/nehalbirla/vehicle-dataset-from-cardekho}{https://www.kaggle.com/datasets/ne-halbirla/vehicle-dataset-from-cardekho}, the predictors are
\begin{itemize}
    \item Year
    \item Present\_price: ex showroom price
    \item Kms Driven
    \item Fuel type
    \item Seller type
    \item Transmission
    \item Owner: number of previous owners
\end{itemize}
The dependent variable is the selling price.

@@

\subsection{Data normalisation}\label{appendix:normalization}
With data normalisation we transform the range of the features to a standard scale.
Such preprocessing step is essential when employing distance based algorithms like SVM or K-nearest neighbours. The rationale behind it is that by normalising data we give an uniform weight to each feature in the learning process; in this way we do not favour larger scale features.
Examples of the most popular features scaling are:
\begin{itemize}
    \item Standard scaler: it computes the standard score $z$ of a sample $x$
    \\
    $z=\frac{x-\mu}{\sigma}$.
    \item MinMax scaler: it maps every data sample to the range $[0,1]$.
    \\
    $\frac{x-\min(X)}{\max(X)-\min(X)}$
    \item Robust scaler: it scales features using statistics that are robust to outliers.
    Essentially, it subtracts the median and then scales the data according to the interquantile range.
\end{itemize}
Many other data scaling algorithms exists, we refer the reader to a thorough comparison \citeW{scikitscalers}.
\\
We conclude this subsection with a custom example that motivates the need of feature scaling \citeW{scikitscale_example}. The idea is to compare the results of modelling the data with K-nearest neighbours on the unscaled data against the scaled data. The considered data is the wine recognition dataset \href{https://archive.ics.uci.edu/dataset/109/wine}{https://archive.ics.uci.edu/da-taset/109/wine}. The goal for this dataset is recognising from whose cultivator the wine comes based on two features with a completely different scale. The first feature has values in the [0,1000] range while the second feature has values contained in [1,10].
The unscaled and scaled version are compared in Figure \ref{fig:feature_scaler_example}.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/feature_scaler_example.png}
    \caption[Importance of feature scaling]{Importance of feature scaling \citeW{scikitscale_example}}
    \label{fig:feature_scaler_example}
\end{figure}
What we can conclude from the image is that, the model trained on scaled data is much better than the other.
On the left, we can see that distances between categories are impacted solely by the larger scale feature. Conversely, on the right, we have that the two features contribute equally in determining the neighbours.

@@

\newpage
\section{Source code}\label{src_code}
The whole code for the project is hosted on
\url{https://github.com/luca-pernigo/ThesisKernelMethods}\label{github_repo}.
\\
\begin{itemize}
    \item query/: folder containing Scopus data and scripts to generate bibliometric survey plots in Section \ref{literature_review}. Database queries have been taken from \cite{nowotarski}.
    \item thesis/: folder containing tex files for thesis pdf.
    \item beamer/: folder containing tex files for beamer pptx %pptx thesis defence.
    \item experiments: folder containing train, test script for each of the experiments carried out in the thesis alongside with the binary files of the pickled models.
    \item experiments/src/kernel\_quantile\_regression/kqr.py: file implementing our custom kernel quantile regression.
    \item experiments/Data: cleaned data used in our experimental studies.
    \item experiment/plots/: folder storing plots resulting from experiments.
    \item experiment/eda/: scripts for exploratory data analysis.
    \item experiments/point/: scripts for experiments point framework.
    \item experiments/train\_test/: scripts for training, testing and generating tables for experiments probabilistic framework.
    \item experiments/utils/: utility functions used in extracting, transforming and cleaning raw data.
    \item extradata/: folder containing data for experiments in section \ref{appendix:quantile_regressor_extensive_comparison}.
    \item requirements.txt: pip freeze of python packages used.
\end{itemize}

>>>>

\section{Feature map normalisation}\label{appendix:new_feature}

\begin{lemma}
    Associated to any RKHS $\mathcal{H}$, there exists a feature vector $\phi(x)$ such that $\|\phi(x)\|_{\mathcal{H}}=R \quad \forall x \in \mathcal{X}$.
    That is the Hilbert space norm of the feature vector is equal to a constant R for all states in the set $\mathcal{X}$.
\end{lemma}

\begin{proof}
    Taking the new feature vector as $\phi^{new} (x):=\frac{\phi(x)}{\|\phi(x)\|_{\mathcal{H}}}$ we have

\begin{align*}
    \|
    \phi^{new}(x)\|_{\mathcal{H}}^{2} &= \left\|\frac{\phi(x)}{\|\phi(x)\|_{\mathcal{H}}}
    \right\|_{\mathcal{H}}^{2}
    \\
    &=
    \left\|
    \frac{\phi(x)}
    {\sqrt{k(x,x)}}
    \right\|_{\mathcal{H}}^{2}
    \\
    &=
    \left\langle
    \frac{\phi(x)}
    {\sqrt{k(x,x)}}
    ,
    \frac{\phi(x)}
    {\sqrt{k(x,x)}}
    \right\rangle_{\mathcal{H}}
    \\
    &=
    \frac{1}{\sqrt{k(x,x)^{2}}}
    \langle
    \phi(x)
    ,
    \phi(x)
    \rangle_{\mathcal{H}}
    \\
    &=1
\end{align*}
\end{proof}

\section{Quantile regressor extensive comparison}\label{appendix:quantile_regressor_extensive_comparison}
This section contains extensive comparison between our kernel quantile regression and other state of the art quantile regressors. We benchmark it on popular machine learning datasets.
\subsection{Boston housing dataset}
The Boston housing dataset \url{https://www.kaggle.com/datasets/altavish/boston-housing-dataset} contains information about various attributes for suburbs in Boston.
There are 13 indipendent variables
\begin{itemize}
\item CRIM: per capita crime rate by town
\item ZN: proportion of residential land zoned for lots over 25,000 sq.ft.\
\item INDUS: proportion of non-retail business acres per town
\item CHAS: Charles River dummy variable (1 if tract bounds river, 0 otherwise)
\item NOX: nitric oxides concentration (parts per 10 million)
\item RM: average number of rooms per dwelling
\item AGE: proportion of owner-occupied units built prior to 1940
\item DIS: weighted distances to five Boston employment centres
\item RAD: index of accessibility to radial highways
\item TAX: full-value property-tax rate per 10,000
\item PTRATIO: pupil-teacher ratio by town
\item B: $1000(Bk - 0.63)^2$ where Bk is the proportion of afroamericans by town
\item LSTAT: lower status of the population
\end{itemize}
The dependent variable is MEDV, that is the median value of owner occupied homes in \$1000's

@@

\subsection{Vehicle dataset}
This data contains info about used cars \url{https://www.kaggle.com/datasets/nehalbirla/vehicle-dataset-from-cardekho}, the predictors are
\begin{itemize}
    \item Year
    \item Present\_price: ex showroom price
    \item Kms Driven
    \item Fuel type
    \item Seller type
    \item Transmission
    \item Owner: number of previous owners
\end{itemize}
The dependent variable is the selling price.

@@

\subsection{Data normalisation}\label{appendix:normalization}
With data normalisation we transform the range of the features to a standard scale.
Such preprocessing step is essential when employing distance based algorithms like SVM or K-nearest neighbours. The rationale behind it is that by normalising data we give an uniform weight to each feature in the learning process; in this way we do not favour larger scale features.
Examples of the most popular features scaling are:
\begin{itemize}
    \item Standard scaler: it computes the standard score $z$ of a sample $x$
    \\
    $z=\frac{x-\mu}{\sigma}$.
    \item MinMax scaler: it maps every data sample to the range $[0,1]$.
    \\
    $\frac{x-\min(X)}{\max(X)-\min(X)}$
    \item Robust scaler: it scales features using statistics that are robust to outliers.
    Essentially, it subtracts the median and then scales the data according to the interquantile range.
\end{itemize}
Many other data scaling algorithms exists, we refer the reader to a thorough comparison \citeW{scikitscalers}.
\\
We conclude this subsection with a custom example that motivates the need of feature scaling \citeW{scikitscale_example}. The idea is to compare the results of modelling the data with K-nearest neighbours on the unscaled data against the scaled data. The considered data is the wine recognition dataset \url{https://archive.ics.uci.edu/dataset/109/wine}. The goal for this dataset is recognising from whose cultivator the wine comes based on two features with a completely different scale. The first feature has values in the [0,1000] range while the second feature has values contained in [1,10].
The unscaled and scaled version are compared in Figure \ref{fig:feature_scaler_example}.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/feature_scaler_example.png}
    \caption[Importance of feature scaling]{Importance of feature scaling \citeW{scikitscale_example}}
    \label{fig:feature_scaler_example}
\end{figure}
What we can conclude from the image is that, the model trained on scaled data is much better than the other.
On the left, we can see that distances between categories are impacted solely by the larger scale feature. Conversely, on the right, we have that the two features contribute equally in determining the neighbours.

@@

\newpage
\section{Source code}\label{src_code}
The whole code for the project is hosted on
\href{https://github.com/luca-pernigo/ThesisKernelMethods}{github repo}.

\begin{itemize}
    \item query/: folder containing Scopus data and scripts to generate bibliometric survey plots in Section \ref{literature_review}. Database queries have been taken from \cite{nowotarski}.
    \item thesis/: folder containing tex files for thesis pdf.
    \item beamer/: folder containing tex files for beamer pptx %pptx thesis defence.
    \item experiments: folder containing train, test script for each of the experiments carried out in the thesis alongside with the binary files of the pickled models.
    \item experiments/src/kernel\_quantile\_regression/kqr.py: file implementing our custom kernel quantile regression.
    \item experiments/Data: cleaned data used in our experimental studies.
    \item experiment/plots/: folder storing plots resulting from experiments.
    \item experiment/eda/: scripts for exploratory data analysis.
    \item experiments/point/: scripts for experiments point framework.
    \item experiments/train\_test/: scripts for training, testing and generating tables for experiments probabilistic framework.
    \item experiments/utils/: utility functions used in extracting, transforming and cleaning raw data.
    \item extradata/: folder containing data for experiments in section \ref{appendix:quantile_regressor_extensive_comparison}.
    \item requirements.txt: pip freeze of python packages used.
\end{itemize}

### 2024-06-04 thesis/input_files/analysis.tex
cleaned all problems and warnings

\subsection{Trigonometric seasonality Box-Cox transformation ARMA errors trend and seasonal components}
Next, we tried with the autoregressive approach. Unfortunately, AR, ARIMA and SARIMA models did not perform as expected, their output was slightly better than the one of linear regression. This is probably due to the fact that, the data considered entails two kinds of seasonalities, while ARIMA models can only handle one at a time. We remind the reader, that the electricity load time series involves both daily and weekly seasonalities. Hence, the need for a more advanced time series model. The Tbats \cite{de2011forecasting} model is a forecasting method capable of handling complex patterns in the data. Its name stands for trigonometric seasonality, Box-Cox transformation, ARMA errors, trend and seasonal components. 
Tbats forecast is visualised in Figure \ref{fig:tbats_price}, meanwhile its RMSE on task 1 is 15.08.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/tbats_price.png}
    \caption{Tbats prediction}
    \label{fig:tbats_price}
\end{figure}
From the plot we see that Tbats is capable of catching the lows and average trend, conversely it has some difficulties handling the price peaks.
\subsection{Prophet}
Following, the prophet model has been considered. 
We get started by considering the base implementation. In such setting, prophet takes as input the time series object and learns its data generating process.
This method achieves on task 1 a RMSE of 23.96, its prediction is visualised in Figure \ref{fig:prophet_price_1}.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/prophet_price_1.png}
    \caption{Prophet prediction}
    \label{fig:prophet_price_1}
\end{figure}
What can be seen is that prophet correctly models the average trend but does not model peaks and lows precisely. 
Next, a more complex model was trained. We added the weather temperature, the square of it and the categorical variable for holidays effect as regressors. Furthermore, we also applied a log transformation to the dependent variables. Doing so, RMSE on task 1 went down to 10.29. Forecast is visualised in Figure \ref{fig:prophet_price2}.
% , moreover figure \ref{fig:prophet_price2.1} and figure \ref{fig:prophet_price2.2} break down the trend and the seasonalities respectively.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/prophet_price2.png}
    \caption{Prophet model\_2 prediction}
    \label{fig:prophet_price2}
\end{figure}

@@

\subsection{K-nearest neighbours}
Afterwards, K-nearest neighbours has been considered. In doing so, we cross validated the number of neighbours to get the best model instance. The forecast is visualised in Figure \ref{fig:knn_price}, RMSE on task 1 is 12.54.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/knn_price.png}
    \caption{K-nearest neighbours regression}
    \label{fig:knn_price}
\end{figure}
What it can be said is that, K-nearest neighbours is capable of predicting load well by averaging past data.

\subsection{Support vector regression}
In applying support vector regression we used gridsearch crossvalidation to search for the best regularisation parameter $C$. Support vector regression achieves on task 1 an RMSE of 23.24, for the prediction see Figure \ref{fig:svr_price}.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/svr_price.png}
    \caption{Support vector regression prediction}
    \label{fig:svr_price}
\end{figure}
Visually, we see that the SVR performs similar to multiple linear regression, as expected. Like multiple linear regression, SVR can model the daily seasonality but the point prediction is off in terms of highs and lows.

\subsection{Long short term memory}\label{sec:lstm point}
We used the \href{https://pytorch.org}{torch} library in order to code our LSTM regressor.
Various hyperparameters combinations were tried during the tuning phase. The final architecture we set on follows
\begin{itemize}
    \item hidden\_size= 64
    \item num\_layers= 2
    \item output\_size= 1
    \item num\_epochs= 30
    \item learning\_rate= 0.001
    \item batch\_size= 32
    \item window\_size= 24
\end{itemize}
LSTM forecast is reported in Figure \ref{fig:lstm_price}, it achieves on task 1 a RMSE of 9.1782
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/lstm_price.png}
    \caption{Long short term memory prediction}
    \label{fig:lstm_price}
\end{figure}

\subsection{Kernel ridge regression}
Subsequently, kernel ridge regression was considered. The kernel considered is the radial basis Gaussian function.
Cross validation was carried jointly over the RBF kernel bandwith and the regularisation constant.
The RMSE achieved on task 1 is 9.86, Figure \ref{fig:krnridge_price} reports the prediction.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/krnridge_price.png}
    \caption{Kernel ridge prediction}
    \label{fig:krnridge_price}
\end{figure}
We can observe that, kernel ridge regression accurately models the electricity time series.

\subsection{Kernel support vector regression}
The last model we considered in this setting was the kernel support vector regression.
RMSE achieved with this method on task 1 is 9.10, forecast is reported in Figure \ref{fig:krnsvr_price}.

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/krnsvr_price.png}
    \caption{Kernel support vector prediction}
    \label{fig:krnsvr_price}
\end{figure}
We can observe that kernel support vector regression is one of the best performing techniques between the ones considered.

@@

\begin{table}[!ht]
    \centering
    \caption{Pinball loss GEFCom2014 price data}
    \label{tab:pinball loss gefcom2014 price data}
    \begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllllll}
      \toprule
      \midrule
      Team name\textbackslash Task number                       & 1                               & 2                                  & 3                               & 4                              & 5                              & 6       & 7                               & 8       & 9       & 10                             & 11                             & 12               \\
  KQR Absolute Laplacian
  &
  \textbf{1.02492}
  &
  3.35057
  &
  4.21374
  &
  7.33987
  &
  5.00981
  &
  6.96522
  &
  3.57168
  &
  1.77610
  &
  1.28765
  &
  2.73863
  &
  2.39831
  &
  23.30234
  \\
  KQR Gaussian RBF
  &
  1.84673
  &
  2.81882
  &
  1.54608
  &
  8.31636
  &
  4.05988
  &
  6.60456
  &
  3.57818
  &
  2.02177
  &
  1.45779
  &
  2.20701
  &
  1.98184
  &
  21.41033
  \\
  \\

@@

\begin{table}[!ht]
    \caption{Pinball loss GEFCom2014 load data}
    \label{tab:pinball loss gefcom2014 load data}
    \begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllllll}
      \toprule
      \midrule
      Team name\textbackslash Task number                       & 1                               & 2                                  & 3                               & 4                              & 5                              & 6       & 7                               & 8       & 9       & 10                             & 11                             & 12                              \\

>>>>

\subsection{Trigonometric seasonality Box-Cox transformation AR\-MA errors trend and seasonal components}
Next, we tried with the autoregressive approach. Unfortunately, AR, ARIMA and SARIMA models did not perform as expected, their output was slightly better than the one of linear regression. This is probably due to the fact that, the data considered entails two kinds of seasonalities, while ARIMA models can only handle one at a time. We remind the reader, that the electricity load time series involves both daily and weekly seasonalities. Hence, the need for a more advanced time series model. The Tbats \cite{de2011forecasting} model is a forecasting method capable of handling complex patterns in the data. Its name stands for trigonometric seasonality, Box-Cox transformation, ARMA errors, trend and seasonal components. 
Tbats forecast is visualised in Figure \ref{fig:tbats_price}, meanwhile its RMSE on task 1 is 15.08.
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/tbats_price.png}
    \caption{Tbats prediction}
    \label{fig:tbats_price}
\end{figure}
From the plot we see that Tbats is capable of catching the lows and average trend, conversely it has some difficulties handling the price peaks.
\subsection{Prophet}
Following, the prophet model has been considered. 
We get started by considering the base implementation. In such setting, prophet takes as input the time series object and learns its data generating process.
This method achieves on task 1 a RMSE of 23.96, its prediction is visualised in Figure \ref{fig:prophet_price_1}.
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/prophet_price_1.png}
    \caption{Prophet prediction}
    \label{fig:prophet_price_1}
\end{figure}
What can be seen is that prophet correctly models the average trend but does not model peaks and lows precisely. 
Next, a more complex model was trained. We added the weather temperature, the square of it and the categorical variable for holidays effect as regressors. Furthermore, we also applied a log transformation to the dependent variables. Doing so, RMSE on task 1 went down to 10.29. Forecast is visualised in Figure \ref{fig:prophet_price2}.
% , moreover figure \ref{fig:prophet_price2.1} and figure \ref{fig:prophet_price2.2} break down the trend and the seasonalities respectively.
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/prophet_price2.png}
    \caption{Prophet model\_2 prediction}
    \label{fig:prophet_price2}
\end{figure}

@@

\subsection{K-nearest neighbours}
Afterwards, K-nearest neighbours has been considered. In doing so, we cross validated the number of neighbours to get the best model instance. The forecast is visualised in Figure \ref{fig:knn_price}, RMSE on task 1 is 12.54.
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/knn_price.png}
    \caption{K-nearest neighbours regression}
    \label{fig:knn_price}
\end{figure}
What it can be said is that, K-nearest neighbours is capable of predicting load well by averaging past data.

\subsection{Support vector regression}
In applying support vector regression we used gridsearch crossvalidation to search for the best regularisation parameter $C$. Support vector regression achieves on task 1 an RMSE of 23.24, for the prediction see Figure \ref{fig:svr_price}.
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/svr_price.png}
    \caption{Support vector regression prediction}
    \label{fig:svr_price}
\end{figure}
Visually, we see that the SVR performs similar to multiple linear regression, as expected. Like multiple linear regression, SVR can model the daily seasonality but the point prediction is off in terms of highs and lows.

\subsection{Long short term memory}\label{sec:lstm point}
We used the \href{https://pytorch.org}{torch} library in order to code our LSTM regressor.
Various hyperparameters combinations were tried during the tuning phase. The final architecture we set on follows
\begin{itemize}
    \item hidden\_size= 64
    \item num\_layers= 2
    \item output\_size= 1
    \item num\_epochs= 30
    \item learning\_rate= 0.001
    \item batch\_size= 32
    \item window\_size= 24
\end{itemize}
LSTM forecast is reported in Figure \ref{fig:lstm_price}, it achieves on task 1 a RMSE of 9.1782
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/lstm_price.png}
    \caption{Long short term memory prediction}
    \label{fig:lstm_price}
\end{figure}

\subsection{Kernel ridge regression}
Subsequently, kernel ridge regression was considered. The kernel considered is the radial basis Gaussian function.
Cross validation was carried jointly over the RBF kernel bandwith and the regularisation constant.
The RMSE achieved on task 1 is 9.86, Figure \ref{fig:krnridge_price} reports the prediction.
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/krnridge_price.png}
    \caption{Kernel ridge prediction}
    \label{fig:krnridge_price}
\end{figure}
We can observe that, kernel ridge regression accurately models the electricity time series.

\subsection{Kernel support vector regression}
The last model we considered in this setting was the kernel support vector regression.
RMSE achieved with this method on task 1 is 9.10, forecast is reported in Figure \ref{fig:krnsvr_price}.
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/krnsvr_price.png}
    \caption{Kernel support vector prediction}
    \label{fig:krnsvr_price}
\end{figure}
We can observe that kernel support vector regression is one of the best performing techniques between the ones considered.

@@

\begin{table}[!ht]
    \centering
    \caption{Pinball loss GEFCom2014 price data}
    \label{tab:pinball loss gefcom2014 price data}
    \begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllllll}
      \toprule
      \midrule
      Team name/Task number                       & 1                               & 2                                  & 3                               & 4                              & 5                              & 6       & 7                               & 8       & 9       & 10                             & 11                             & 12               \\
  KQR Absolute Laplacian
  &
  \textbf{1.02492}
  &
  3.35057
  &
  4.21374
  &
  7.33987
  &
  5.00981
  &
  6.96522
  &
  3.57168
  &
  1.77610
  &
  1.28765
  &
  2.73863
  &
  2.39831
  &
  23.30234
  \\
  KQR Gaussian RBF
  &
  1.84673
  &
  2.81882
  &
  1.54608
  &
  8.31636
  &
  4.05988
  &
  6.60456
  &
  3.57818
  &
  2.02177
  &
  1.45779
  &
  2.20701
  &
  1.98184
  &
  21.41033
  \\
  \\

@@

\begin{table}[!ht]
    \caption{Pinball loss GEFCom2014 load data}
    \label{tab:pinball loss gefcom2014 load data}
    \begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllllll}
      \toprule
      \midrule
      Team name/Task number                       & 1                               & 2                                  & 3                               & 4                              & 5                              & 6       & 7                               & 8       & 9       & 10                             & 11                             & 12                              \\
